### 2014-06-30 Docs/mg/mg.tex
some info on the various multifabs

>>>>

\item {\tt ss}: The stencil itself---for each zone, this gives the 
  coefficients of the terms in the Laplacian, with the convection that
  the `0' term is located in the current cell and the other terms are
  the $\pm 1$ off the current cell in each direction.

\item {\tt cc}: scratch space (?)

\item {\tt ff}: The source (righthand side) of the elliptic equation
  we are solving.

\item {\tt dd}: The residual/defect, $ff - L\phi$

\item {\tt uu}: The solution variable ($\phi$ when on the finest level)

\item {\tt mm}: A mask used at coarse/fine interfaces
\end{itemize}
